### 2021-01-11 msc-thesis.tex
.

    \item \textbf{Status update to portal}

    The form-server sends updates to the administration portal regarding the current status of the application. The possible status updates are listed in the interface section.

@@

    If the administration portal submitted personal data to the form-server, the form can automatically be filled in. This can be done because both the user profile and the form-server use the same data fields defined through FIM.

@@

    The form can be integrated into the administration portal through for example an URL or Web-Component.

@@

    Depending on the actions of the user, the status of the application changes accordingly and the administration portal is notified through a status update.

    \item \textbf{Storage of application}

    The form-server stores applications for a specified period of time if they were interrupted or submitted. In case of submission, the administration portal notifies the form server, if the application can be deleted.

@@

    The administration portal submits JWT to the form-server which corresponds to a user profile. Based on this information, the form-server searches all stored applications which belong to the user profile and sends back to the portal a list of URLs, through which the user can access them.

@@

    If requested by the administration portal, the form-server can delete stored applications. This is usually the case after an application was submitted to the administration portal.

@@

    The user can add documents as attachments to an application. Uploaded documents are scanned for viruses.

    \item \textbf{Authentication of user profile}

    JSON web token from administration portal.

@@

    When the user submits the application by for example pressing a "submit" button, the form-server notifies the administration portal through a status update. The administration portal can then continue processing the application by requesting the application data from the form server. The portal does this by sending the form-server a FMS-ID it was sent by the form-server with the first status update.

@@

    Personal information of the user profile can be managed through the administration portal after successful authentication.

    \item \textbf{Provisioning Personal Information to Form-Server} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}

    If a user selects to open the form of an administrative service which is integrated in the administration portal, the portal asks the user for permission to transmit personal information to the form-server. If the user is logged in and accepts, the administration portal retrieves the necessary personal information from the user profile and forwards it to the form-server.

@@

\paragraph{Data Wallet}

\paragraph{Inbox}

\subsubsection{Interfaces}
In order to implement the basic use case, the components have to interact with each. The following diagram visualizes, which components interact. Each interaction is described afterwards.

@@

\begin{enumerate}
    \item The user interacts with the system architecture relevant for OZG only through the administration portal. The user is provided with a website as an interface with multiple online self-service functionalities.
    \item Administration portal and form-server interact through a REST API. The API provides the following interfaces:
    \begin{itemize}
        \item \textbf{Application initiation interface provided by form-server and used by administration portal}

@@

            \hline
            \end{tabularx}
            \caption{Interface of the form-server for initialization of an application}
            \label{table:interface_form_initialization}
        \end{table}
        \item \textbf{Status updates from from-server to administration portal}

@@

            \hline
            \end{tabularx}
            \caption{Interface of the form-server for requesting application data by the administration portal.}
            \label{table:interface_application_data}
        \end{table}
    \end{itemize}

@@

>>>>

    \item \textbf{Status update}

    The form-server sends updates regarding the current status of the application.

@@

    If the form server was provided with personal information during the initiation request for an application, it can automatically fill in the form.

@@

    The form server can host a website where it displays an interactive form. The user can access this website either through an URL or through a web component.

@@

    Depending on the actions of the user, the status of the application changes accordingly and the form server sends an status update.

    \item \textbf{Storage of application}
    The form-server stores applications for a specified period of time if they were interrupted or submitted.

@@

    If the form server is provided an identification and authorisation of a user, it searches all stored applications which belong to the user and sends back a list of URLs, through which the user can access them.

@@

    If the form server is provided an identification and authorisation of a user and an identification of an application, it can delete the stored application.

@@

    The user can add documents as attachments to an application. The documents can either be uploaded from the local machine or the data wallet of the user profile.

@@

    When the user submits the application by for example pressing a "submit" button, the form-server sends a status update. The finished application can now be transmitted to a requesting system.

@@

    Personal information of the user profile can be managed through the administration portal after successful authentification.

    \item \textbf{Provisioning Personal Information} \cite{dNRW:Anbindungsleitfaden} \cite{dNRW:Schnittstellen}

    The user profile can be requested to send personal information to a specified URL. This requires the user to authenticate.

@@

\paragraph{Data Wallet}
The data wallet is a sub-component of the user profile and enables the user to manage documents for his user profile. The main services are:

\begin{itemize}

    \item \textbf{Upload of document}

    The user can upload a document from his local machine to the data wallet.

    \item \textbf{Show documents}

    The user can list all documents which are stored in the data wallet.

    \item \textbf{Delete documents}

    The user can delete documents from the data wallet.

    \item \textbf{Attach documents to application}

    The user can attach a copy of a document stored in his data wallet to an application on a from server.

\paragraph{Inbox}
The inbox is a sub-component of the user profile and enables the user to send messages through his user profile. The main services are:

\begin{itemize}

    \item \textbf{Send a message}

    The user can send a message to authorities. This can be for example an institution which processes an application.

    \item \textbf{Receive a message}

    The user can receive messages from authorities for example to update the status of an application.

    \item \textbf{List messages}

    The user can see the messages he received by logging in to his user profile on the administration portal.

    \item \textbf{Notification through E-Mail}

    The user can be notified of a new message through E-Mail.

\subsubsection{Interfaces}
In order to implement the basic use case, the components have to interact with each. The following diagram visualizes, which components interact. Each interaction is described afterwards. The arrows describe the main direction of information flow in an interaction.

@@

\begin{enumerate}

    \item The form-server provides the service "Initiation of application" which can be requested by the administration portal. The portal submits information for identification, authentication and authorisation of a user through an JSON Web Token and a user profile ID. In order for the form server to determine the correct form to display, the portal submits a FIM-ID which corresponds to a data field schemata. In case the user approved, the portal can also collect personal information from the user profile and submit it to the form server for automated filling in of the form.

    \item The user interacts with the system architecture relevant for OZG only through the administration portal. The user is provided with a website as an interface with multiple online self-service functionalities.
    \item Administration portal and form-server interact through a REST API. The API provides the following interfaces:
    \begin{itemize}
        \item \textbf{Application initiation interface provided by form-server and used by administration portal}

@@

        \item \textbf{Status updates from from-server to administration portal}

@@

@@

\chapter{Tables}

            \hline
            \end{tabularx}
            \caption{Interface of the form-server for initialization of an application}
            \label{table:interface_form_initialization}
        \end{table}

            \hline
            \end{tabularx}
            \caption{Interface of the form-server for requesting application data by the administration portal.}
            \label{table:interface_application_data}
        \end{table}
